Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
why we take recent years only

The data set used in this study~\cite{msr17challenge} is very diverse.
and consists of commits from multiple\todo{How many? Please be precise.} years ago. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  While this is not
a perfect solution , we believe that these numbers are unlikely to have changed
significantly in the last three years.\todo{Why?}

>>>>

The data set used in this study~\cite{msr17challenge} is very diverse.
and consists of commits from multiple\todo{How many? Please be precise.} years ago. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  This is with the intuition that the social attributes are more likely to have similar values in the most recent years than if we were to consider the whole time span of the projects in the data set.
